Application-Level Regression Testing Framework using Jenkins

### 2017-03-08 manuscript/manuscript.tex
anatomy of a test
added subsections

\section{Anatomy of A Test}
\label{sec:TestAnatomy}
New software projects are required to be tested on our TDS and approved before deployment on Blue Waters.

@@

\section{Conclusion}
\label{sec:conclusion}

>>>>

\section{Anatomy of A Test}
\label{sec:TestAnatomy}
New software projects are required to be tested on our TDS and approved before deployment on Blue Waters and this is one of our key best practices.  Once a test is deployed it is assigned to a specific Jenkins tab via the "Edit View" link associated with that tab.  Tests still in development reside in the "All" tab view until they have been peer reviewed by at least one other test developer.
\subsection{test description}
We require a description for each test to describe: what is tested, resources used by the test, intent of the test, and scheduling frequency.
\subsection{limits log files}
The Jenkins test VM filled to capacity after the first few weeks of intensive use and an influx of several new tests that output long source code build detail.  We retroactively modified all tests to limit the number of old build logs retained (max 50 for most tests). 
\subsection{ssh to a login host}
There are several target ssh hosts which may be selected from our instance: the test rack JYC, the main system, and the new software deployment login node within the main system.  None of our tests run locally within the Jenkins VM.
\subsection{run shell commands}
A test is composed of shell command and where possible we try to be as transparent with our test construction as possible.  We prefer commands in the Jenkins configuration over running a script in the filesystem on the remote ssh target.  Scripts that are remote run with verbose mode or are displayed via "cat -n" to save output to the Jenkins console log and make for simpler debugging when a test fails.
\subsubsection{test completes on login node}
Some tests run only on the ssh login node and return more or less immediately.  Examples include tests for batch system functionality, ssh functionality, and filesystem functionality.  These tests are very similar in style to unit tests which target a limited set of functionality.
\subsubsection{test is submitted to batch system}
More comprehensive tests typically build and run an application or benchmark through the batch system.  These tests exercise multiple aspects of the system: (filesystem, compilers and modules, high-speed network, external connectivity to the internet...).  They block to completion so that we do not overburden the batch system with tests.  Unlike tests that run entirely on a login node, completion time can be highly variable depending on the queue depth and available backfill windows for the batch system.
\subsection{post test actions}
\subsubsection{scp files back to Jenkins host}
Most comprehensive tests produce output that we use when debugging a failed test.  They may also produce plot data.  These files are copied back to the Jenkins host so that they can be viewed and/or incorporated into the plot feature of Jenkins.
\subsubsection{plots}
Successful tests save plot files and contribute a new data point to a plot.  The Jenkins server accumulates the data as rows in a spreadsheet (under /var/lib/jenkins/jobs/ ) and plots them via the "Plots" link for a test.
\subsection{email notification}
When the state of a test changes, email notification is sent to the test owner.  As a best practice we also use the email notification as a method of tracking authorship and each test has an email owner even if notifications are disabled for the test.

@@

\section{Conclusion}
\subsection{caveats}
Transient errors with Jenkins sometimes occur--particularly with the Jenkins ssh subsystem.  It's not unusual to get failure rates of 1/100 from an ssh failure which is completely transient (immediately running the test again manually clears the issue on the dashboard).
\label{sec:conclusion}
